### 2015-07-14 fundamentals/fcsreqs.tex
Fixes #116, using comments from @rwcarlsen

Many fuel cycle phenomena have aggregate system-level effects which can only be
captured by discrete material tracking \cite{huff_next_2010}.  \Cyclus
tracks materials as discrete objects. Some current fuel cycle simulation tools
such as \gls{COSI}
\cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
FAMILY21\cite{mccarthy_benchmark_2012},
\gls{GENIUS} version 1, \gls{GENIUS} version 2, \gls{NFCSim}, and ORION also 
possess the ability to model discrete materials.

Similarly, the ability to model disruptions (i.e. facility shutdowns due to
insufficient feed material or insufficient processing and storage capacity) is
most readily captured by software capable of tracking the operations status of
discrete facilities \cite{huff_next_2010}.  Fleet-based models (e.g.
\gls{VISION}) are unable to capture this gracefully, perhaps representing it as
a reduction in the capacity of the whole fleet.  All of the software
capable of discrete materials have a notion of discrete facilities, however not
all handle disruption in the same manner. \gls{DESAE}, for example, does not
allow shutdown due to insufficient feedstock. In the event
of insufficient fissile material during reprocessing, \gls{DESAE} borrows
material from storage, leaving a negative value \cite{mccarthy_benchmark_2012}.
The \Cyclus framework does not dictate such heuristics. Rather, it provides a
flexible framework on which either method is possible.

>>>>

Many fuel cycle phenomena have aggregate system-level effects which can only be
captured by discrete material tracking \cite{huff_next_2010}.  \Cyclus
tracks materials as discrete objects. Some current fuel cycle simulation tools
such as \gls{COSI}
\cite{mccarthy_benchmark_2012,grasso_nea-wpfc/fcts_2009,guerin_benchmark_2009},
FAMILY21\cite{mccarthy_benchmark_2012},
\gls{GENIUS} version 1, \gls{GENIUS} version 2, \gls{NFCSim}, and ORION also
possess the ability to model discrete materials. However, even among these, the ability to model reactor facilities individually is not equivalent to the ability to model distinct activities. \gls{COSI}, for example,
has some support for modeling reactors individually, but according to a recent benchmark \cite{oecd_benchmark_2012}, it models many reactors operating in sync. That is, refuelling and discharging occur simultaneously for all reactors.
While \Cyclus allows this type of fleet-based aggregation of reactor behavior, \Cyclus also enables operations in each facility to vary independently of any others in the simulation.

Similarly, the ability to model disruptions (i.e. facility shutdowns due to
insufficient feed material or insufficient processing and storage capacity) is
most readily captured by software capable of tracking the operations status of
discrete facilities \cite{huff_next_2010}.  Fleet-based models (e.g.
\gls{VISION}) are unable to capture this gracefully, since supply disruptions
are modeled as a reduction in the capacity of the whole fleet.  All of the
software capable of discrete materials have a notion of discrete facilities,
however not all handle disruption in the same manner. \gls{DESAE}, for example,
does not allow shutdown due to insufficient feedstock. In the event of
insufficient fissile material during reprocessing, \gls{DESAE} borrows material
from storage, leaving a negative value \cite{mccarthy_benchmark_2012}.  The
\Cyclus framework does not dictate such heuristics. Rather, it provides a
flexible framework on which either method is possible.

A final benefit of the discreteness of facilities and materials is their power
when combined. The ability to track a material's history as it moves from one
facility to another is unique to \Cyclus. While some current simulators track
materials in chunks, they do not necessarily preserve chunk identity as the
materials move around the fuel cycle. When coupled with \Cyclus' individual
facility modeling, this capacity becomes distinct from what other fuel cycle
simulators are able to do. So, while FAMILY21 and \gls{COSI} can identify
whether a batch being discharged from a reactor originated in \gls{MOX}
fabrication rather than fresh \gls{UOX} fabrication, \Cyclus can go further,
tracking which of the fresh batches contained material from a particular
discharged batch. By extension, \Cyclus can also report which individual
facilities the batch passed through and in which it originated. The
nonproliferation-related applications of this analysis capability are
significant - allowing \Cyclus to answer questions that previous simulators
have been unable to ask.
